---
title: "lab10_key"
author: "Mari Herbst"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attach packages
library(tidyverse)
library(usethis)
library(janitor)
library(here)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr beeps

Use the function 'beep()' in the beepr package to make an audio alert when your code is done running.

```{r}
for (i in rev(seq(1:999))) {
  print(paste(i, "bottles of beer on the wall"))
} # for each element in this vector, print the number plus this string

# add beep(x) to be notified when the code is done running
```

## praise and cowsay

Packages built with a single purpose: to be kind and fun

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}")
```

Use cowsay:say() to make a character say something to you

```{r}
say("Hi", by = "cow")
```

## usethis

usethis::edit_r_profile to change the greeting animal or phrase when RStudio opens

usethis::use_git() converts a non version controlled Rproj into a local git project (still only lives on this computer)

usethis::use_github() turns the local git project into a remote github repo with version control

## use paletteer to access thousands of color palettes

```{r}
storms %>%
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>% # refine to the 10 storms w lowest pressure
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("ggprism::floral2")
```

## One spatial data example

```{r}
vegetation <- read_sf(here("data", "doc.kml")) %>%
  select(Name) %>%
  clean_names()

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) + # fill color change based on dominant vegetation type, color of line to NA
  theme_minimal() + # update theme to theme_minimal
  scale_fill_paletteer_d("ggthemes::manyeys") + # select color scheme
  labs(totle = "Jornada Basin LTER Vegetation",
       caption = "Source: Jornada LTER")
```

```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5) # save the last created ggplot
```

